Models with year

### 2022-10-07 Rmd/model_with_year.Rmd
fruit proportion and year

\newpage
Predicte values of seed number
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
mod_seed_year.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(Seeds~visitatio_rate * Year,data)))

ggarrange(plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE), ncol=3,nrow = 4)

@@

>>>>

\newpage
Predicte values of seed number
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p1=plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus",show.data = TRUE)
p2=plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus",show.data = TRUE)
p3=plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer",show.data = TRUE)
p4=plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis",show.data = TRUE)
p5=plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis",show.data = TRUE)
p6=plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius",show.data = TRUE)

p1.1=plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
p2.1=plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
p3.1=plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
p4.1=plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
p5.1=plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis",show.data = TRUE)
p6.1=plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)

ggarrange(p1$visitatio_rate,p1$Year,p1.1,
p2$visitatio_rate,p2$Year,p2.1,
p3$visitatio_rate,p3$Year,p3.1,
p4$visitatio_rate,p4$Year,p4.1,
p5$visitatio_rate,p5$Year,p5.1,
p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p7=plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum",show.data = TRUE)
p8=plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium",show.data = TRUE)
p9=plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata",show.data = TRUE)
p10=plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas",show.data = TRUE)
p11=plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus",show.data = TRUE)
p12=plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans",show.data = TRUE)

p7.1=plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
p8.1=plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
p9.1=plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
p10.1=plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
p11.1=plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
p12.1=plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)

ggarrange(p7$visitatio_rate,p7$Year,p7.1,
p8$visitatio_rate,p8$Year,p8.1,
p9$visitatio_rate,p9$Year,p9.1,
p10$visitatio_rate,p10$Year,p10.1,
p11$visitatio_rate,p11$Year,p11.1,
p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)

@@

\newpage
**Richness **

**A-** linear model: lm(Seeds ~ richness * Year)

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
# linear model 
mod_seed_year_richness<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(Seeds ~ richness * Year,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

mod_seed_year_richness<-mod_seed_year_richness %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed_year_richness %>% 
 kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
column_spec(6, bold = ifelse(mod_seed_year_richness$p.value < 0.05| is.na(mod_seed_year_richness$p.value), T, F) )%>%
  kable_styling(position="left")

\newpage
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
#model plot
mod_seed_year_richness.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(Seeds ~ richness * Year,data)))

ggarrange(plot_model(mod_seed_year_richness.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
plot_model(mod_seed_year_richness.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)

ggarrange(plot_model(mod_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)

#model
mod_mix_seed_year_richness<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds ~ richness * Year + (1 | Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_mix_seed_year_richness<-mod_mix_seed_year_richness %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_mix_seed_year_richness<-filter(mod_mix_seed_year_richness, !term == "sd__(Intercept)" & !term =="sd__Observation")

mod_mix_seed_year_richness %>% 
 kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
column_spec(7, bold = ifelse(mod_mix_seed_year_richness$p.value < 0.05, T, F) )%>%  kable_styling(position="left")

\newpage
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
#model plot
mod_mix_seed_year_richness.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lmer(Seeds ~ richness * Year + (1 | Site_ID),data)))

ggarrange(plot_model(mod_mix_seed_year_richness.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
plot_model(mod_mix_seed_year_richness.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)

ggarrange(plot_model(mod_mix_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_mix_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)

# Fruit proportion

**visitation rate (all pollinator)**

**A-** GLM binomial (cbind(fruit_formado, Fruit_No))

mod_fruit_year<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ visitatio_rate * Year,data,family = binomial))) %>%
  summarize(tidy(mod))%>%
  ungroup()

mod_fruit_year<-mod_fruit_year %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruit_year %>% 
 kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
column_spec(6, bold = ifelse(mod_fruit_year$p.value < 0.05| is.na(mod_fruit_year$p.value), T, F) )%>%
  kable_styling(position="left")

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
mod_fruit_year.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ visitatio_rate * Year,data,family = binomial)))

p1=plot_model(mod_fruit_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
p2=plot_model(mod_fruit_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_fruit_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_fruit_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_fruit_year.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
p6=plot_model(mod_fruit_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_fruit_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
p2.1=plot_model(mod_fruit_year.1$mod[[2]], type = "int", title = " Cistus crispus")
p3.1=plot_model(mod_fruit_year.1$mod[[3]], type = "int", title = " Cistus ladanifer")
p4.1=plot_model(mod_fruit_year.1$mod[[4]], type = "int",title = "Cistus libanotis")
p5.1=plot_model(mod_fruit_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
p6.1=plot_model(mod_fruit_year.1$mod[[6]], type = "int",title = " Cistus salviifolius")

ggarrange(p1$visitatio_rate,p1$Year,p1.1,
p2$visitatio_rate,p2$Year,p2.1,
p3$visitatio_rate,p3$Year,p3.1,
p4$visitatio_rate,p4$Year,p4.1,
p5$visitatio_rate,p5$Year,p5.1,
p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p7=plot_model(mod_fruit_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_fruit_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_fruit_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_fruit_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_fruit_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_fruit_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_fruit_year.1$mod[[7]], type = "int",title = " Halimium calycinum")
p8.1=plot_model(mod_fruit_year.1$mod[[8]], type = "int",title = " Halimium halimifolium")
p9.1=plot_model(mod_fruit_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
p10.1=plot_model(mod_fruit_year.1$mod[[10]], type = "int",title = " Lavandula stoechas")
p11.1=plot_model(mod_fruit_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
p12.1=plot_model(mod_fruit_year.1$mod[[12]], type = "int",title = " Teucrium fruticans")

ggarrange(p7$visitatio_rate,p7$Year,p7.1,
p8$visitatio_rate,p8$Year,p8.1,
p9$visitatio_rate,p9$Year,p9.1,
p10$visitatio_rate,p10$Year,p10.1,
p11$visitatio_rate,p11$Year,p11.1,
p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)

```
\newpage

**B-** GLMM binomial (ramdon= Site_ID)

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

# glmm binomial
mod_mix_fruit_year<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate *Year + (1|Site_ID),data,family = binomial))) %>%
  summarize(tidy(mod))%>%
  ungroup()

mod_mix_fruit_year<-mod_mix_fruit_year %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_mix_fruit_year<-filter(mod_mix_fruit_year, !term == "sd__(Intercept)")

mod_mix_fruit_year %>% 
kable("latex",booktabs = TRUE,digits =  4,longtable = T, linesep = "") %>% column_spec(6, bold = ifelse(mod_mix_fruit_year$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
mod_mix_fruit_year.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate *Year + (1|Site_ID),data,family = binomial)))

p1=plot_model(mod_mix_fruit_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
p2=plot_model(mod_mix_fruit_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_mix_fruit_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_mix_fruit_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_mix_fruit_year.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
p6=plot_model(mod_mix_fruit_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_mix_fruit_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
p2.1=plot_model(mod_mix_fruit_year.1$mod[[2]], type = "int", title = " Cistus crispus")
p3.1=plot_model(mod_mix_fruit_year.1$mod[[3]], type = "int", title = " Cistus ladanifer")
p4.1=plot_model(mod_mix_fruit_year.1$mod[[4]], type = "int",title = "Cistus libanotis")
p5.1=plot_model(mod_mix_fruit_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
p6.1=plot_model(mod_mix_fruit_year.1$mod[[6]], type = "int",title = " Cistus salviifolius")

ggarrange(p1$visitatio_rate,p1$Year,p1.1,
p2$visitatio_rate,p2$Year,p2.1,
p3$visitatio_rate,p3$Year,p3.1,
p4$visitatio_rate,p4$Year,p4.1,
p5$visitatio_rate,p5$Year,p5.1,
p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)

\newpage
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p7=plot_model(mod_mix_fruit_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_mix_fruit_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_mix_fruit_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_mix_fruit_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_mix_fruit_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_mix_fruit_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_mix_fruit_year.1$mod[[7]], type = "int",title = " Halimium calycinum")
p8.1=plot_model(mod_mix_fruit_year.1$mod[[8]], type = "int",title = " Halimium halimifolium")
p9.1=plot_model(mod_mix_fruit_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
p10.1=plot_model(mod_mix_fruit_year.1$mod[[10]], type = "int",title = " Lavandula stoechas")
p11.1=plot_model(mod_mix_fruit_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
p12.1=plot_model(mod_mix_fruit_year.1$mod[[12]], type = "int",title = " Teucrium fruticans")

ggarrange(p7$visitatio_rate,p7$Year,p7.1,
p8$visitatio_rate,p8$Year,p8.1,
p9$visitatio_rate,p9$Year,p9.1,
p10$visitatio_rate,p10$Year,p10.1,
p11$visitatio_rate,p11$Year,p11.1,
p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)

\newpage
**visitation rate of *Apis mellifera* **

**A-** GLM binomial (cbind(fruit_formado, Fruit_No))

# glm binomial
mod_fruit_year_apis<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Apis_visit_rate * Year,data,family = binomial))) %>%
  summarize(tidy(mod))%>%
  ungroup()

mod_fruit_year_apis<-mod_fruit_year_apis %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruit_year_apis %>% 
 kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
column_spec(6, bold = ifelse(mod_fruit_year_apis$p.value < 0.05| is.na(mod_fruit_year_apis$p.value), T, F) )%>%
  kable_styling(position="left")

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
#model plot
mod_fruit_year_apis.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Apis_visit_rate * Year,data,family = binomial)))

p1=plot_model(mod_fruit_year_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
p2=plot_model(mod_fruit_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_fruit_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_fruit_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_fruit_year_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
p6=plot_model(mod_fruit_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_fruit_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
p2.1=plot_model(mod_fruit_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
p3.1=plot_model(mod_fruit_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
p4.1=plot_model(mod_fruit_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
p5.1=plot_model(mod_fruit_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
p6.1=plot_model(mod_fruit_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")

ggarrange(p1$Apis_visit_rate,p1$Year,p1.1,
p2$Apis_visit_rate,p2$Year,p2.1,
p3$Apis_visit_rate,p3$Year,p3.1,
p4$Apis_visit_rate,p4$Year,p4.1,
p5$Apis_visit_rate,p5$Year,p5.1,
p6$Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)

\newpage
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p7=plot_model(mod_fruit_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_fruit_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_fruit_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_fruit_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_fruit_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_fruit_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_fruit_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
p8.1=plot_model(mod_fruit_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
p9.1=plot_model(mod_fruit_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
p10.1=plot_model(mod_fruit_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
p11.1=plot_model(mod_fruit_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
p12.1=plot_model(mod_fruit_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")

ggarrange(p7$Apis_visit_rate,p7$Year,p7.1,
p8$Apis_visit_rate,p8$Year,p8.1,
p9$Apis_visit_rate,p9$Year,p9.1,
p10$Apis_visit_rate,p10$Year,p10.1,
p11$Apis_visit_rate,p11$Year,p11.1,
p12$Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)

\newpage
**B-** GLMM binomial (ramdon= Site_ID)

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

# glmm binomial
mod_mix_fruit_year_apis<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate *Year + (1|Site_ID),data,family = binomial))) %>%
  summarize(tidy(mod))%>%
  ungroup()

mod_mix_fruit_year_apis<-mod_mix_fruit_year_apis %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_mix_fruit_year_apis<-filter(mod_mix_fruit_year_apis, !term == "sd__(Intercept)")

mod_mix_fruit_year_apis %>% 
kable("latex",booktabs = TRUE,digits =  4, longtable = T,linesep ="") %>% 
column_spec(6, bold = ifelse(mod_mix_fruit_year_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
#model plot
mod_mix_fruit_year_apis.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate *Year + (1|Site_ID),data,family = binomial)))

p1=plot_model(mod_mix_fruit_year_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
p2=plot_model(mod_mix_fruit_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_mix_fruit_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_mix_fruit_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_mix_fruit_year_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
p6=plot_model(mod_mix_fruit_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_mix_fruit_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
p2.1=plot_model(mod_mix_fruit_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
p3.1=plot_model(mod_mix_fruit_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
p4.1=plot_model(mod_mix_fruit_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
p5.1=plot_model(mod_mix_fruit_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
p6.1=plot_model(mod_mix_fruit_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")

ggarrange(p1$Apis_visit_rate,p1$Year,p1.1,
p2$Apis_visit_rate,p2$Year,p2.1,
p3$Apis_visit_rate,p3$Year,p3.1,
p4$Apis_visit_rate,p4$Year,p4.1,
p5$Apis_visit_rate,p5$Year,p5.1,
p6$Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)

\newpage
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p7=plot_model(mod_mix_fruit_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_mix_fruit_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_mix_fruit_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_mix_fruit_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_mix_fruit_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p11=plot_model(mod_mix_fruit_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_mix_fruit_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
p8.1=plot_model(mod_mix_fruit_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
p9.1=plot_model(mod_mix_fruit_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
p10.1=plot_model(mod_mix_fruit_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
p11.1=plot_model(mod_mix_fruit_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
p12.1=plot_model(mod_mix_fruit_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")

ggarrange(p7$Apis_visit_rate,p7$Year,p7.1,
p8$Apis_visit_rate,p8$Year,p8.1,
p9$Apis_visit_rate,p9$Year,p9.1,
p10$Apis_visit_rate,p10$Year,p10.1,
p11$Apis_visit_rate,p11$Year,p11.1,
p12$Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)

\newpage
**visitation rate of pollinator without *Apis mellifera* **
